\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-10-30 doc/acknowledgments.tex
A few notes etc

We are also grateful to Brooke Simmons, David Hogg, XXX and YYY for many useful
conversations about citizen science and gravitational lens detection. 
%
PJM was given support by the Royal Society, in the form of a research
fellowship, and by the U.S. Department of Energy under contract number DE-AC02-76SF00515.
%
AV acknowledges support from the Leverhulme Trust in the form of a research
fellowship.
%
The work of AM and SM was supported by World Premier International Research
Center Initiative (WPI Initiative), MEXT, Japan.
%
% Zooniverse / Sloan Foundation.
% 
% Other authors.
%
The \sw project is open source. 
The web app was developed at https://github.com/Zooniverse/Lens-Zoo
while the SWAP analysis software was developed at
https://github.com/drphilmarshall/SpaceWarps.

>>>>

We are also grateful to Brooke Simmons, David Hogg, XXX and YYY for many useful
conversations about citizen science and gravitational lens detection. 
%
PJM was given support by the Royal Society, in the form of a research
fellowship, and by the U.S. Department of Energy under contract number DE-AC02-76SF00515.
%
AV acknowledges support from the Leverhulme Trust in the form of a research
fellowship.
%
The work of AM and SM was supported by World Premier International Research
Center Initiative (WPI Initiative), MEXT, Japan. The work of AM was also supported in
part by National Science Foundation Grant No. PHYS-1066293 and the hospitality
of the Aspen Center for Physics. 
%
% Zooniverse / Sloan Foundation.
% 
% Other authors.
PJM and ES thank the Institute of Astronomy and Astrophysics, Academia Sinica
(ASIAA) and Taiwan's Ministry of Science and Technology (MOST) for their
financial support of the workshop ``Citizen Science in Astronomy'' in March
2014, at which some parts of the SWAP analysis was developed.

The \sw project is open source. 
The web app was developed at https://github.com/Zooniverse/Lens-Zoo
while the SWAP analysis software was developed at
https://github.com/drphilmarshall/SpaceWarps.

### 2014-10-30 doc/sw-publication-policy-gen.tex

\title{Guidelines and Policy for Surveys using \SW}
\author{Phil Marshall, Aprajita Verma \& Anupreeta More}
\date{April 15, 2013}
\maketitle

@@

>>>>

\title{Guidelines and Policy for Surveys using \SW}
\author{Phil Marshall, Aprajita Verma \& Anupreeta More}
\date{October 27, 2014}
\maketitle

@@

\vspace{2mm}
The PIs of the \sw project are the authors of this document, P.\,Marshall, 
A.\,More and A.\,Verma, please do not hesitate to contact us if you require any further information or have any questions. The PIs may be collectively contacted via the email address \href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com}

### 2014-10-30 doc/sw-system.tex

The stage 1 curves are truncated by the retirement of subjects in this phase, 
which sets the minimum size of this sample. We see from the solid blue curve
that over 90\% completeness was reached, albeit in a sample with around 20\%
purity. To investigate the completeness to the three different types of lens
in the training set, we ...

\todo{Chris}{complete the above sentence to explain what purity means in the
divided-by-sim-type case. Thanks! \#66}

@@

The optimal sample in this simulated lens search experiment would have been
constructed with a threshold value of $\pr(\LENS|C,T) > X.XX$. At 100\% purity
and 9X\% completeness, it would have contained around N lens candidates.

\todo{Chris}{fill in the numbers above, please! :-) \#65}

>>>>

The stage 1 curves are truncated by the retirement of subjects in this phase, 
which sets the minimum size of this sample. We see from the solid blue curve
that over 90\% completeness was reached, albeit in a sample with around 20\%
purity. To investigate the completeness to the three different types of lens
in the training set, we repeat the same procedure, only now we consider only
the detections of a certain kind of lens and of the non-lenses in the training
set. We estimate the expected number of lenses and non-lens false positives by
dividing the lens and dud sets into equal fractions.

\todo{Chris}{That still could be worded better... \# 66}

@@

The optimal sample in this simulated lens search experiment would have been
constructed with a threshold value of $\pr(\LENS|C,T) > 0.47$. At 100\% purity
and 89\% completeness, it would have contained around 89 lens candidates.
% TP + FN ~ 2e-4 * 430000 ~ 100 ~ TP/C ; so TP ~ 89 candidates
